---
title: "Rmarkdown_example1"
author: "Avighan Majumder"
date: "November 28, 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

##My New Slide
Some content on it

*** 
A slide without a title

## My title with 2 pound sign
###Subheading slide with 3 pound sign - A top level subheading
#### Second level subheading with 4 pound sign

- Bullet a
- Bullet b

1. Item1
2. Item2
3. Item3


## Formatting Options

*italicized text*

**Bold text**

`for (i %in% 1:10)`


## R code that is going to run
```{r}
head(mtcars)
```
###Removing the comment
```{r,comment=""}
head(mtcars)
```

## Showing the code using echo as True
```{r,comment="",echo=TRUE}
head(mtcars)
```


## Showing a plot
```{r,echo=FALSE,fig.cap="My awesome figure",fig.align='center'}
plot(mtcars$wt,mtcars$mpg,xlab="weight",ylab = "MPG")

```


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

